Make any stupid plot you want

### 2021-05-03 draft/sections/next.tex
discussion section

\begin{document}
\section{Discussion}
This work contributes a functional model of the structure-preserving maps from data to visual representation to guide the development of visualization libraries, thereby providing a means to express the constraints that visualization must preserve continuity and faithfully translate the properties of the data variables into visual variables. Combining Butler's proposal of a fiber bundle model of visualization data with Spivak's formalism of schema lets this model support a variety of datasets, including  discrete relational tables, multivariate high resolution spatio temporal datasets, and complex networks. By decomposing the artist into encoding \vchannel, assembly \vmark, and reindexing \vindex\ maps, the model expresses the specifications that graphic and data must have equivalent \textit{continuity} equivalent to the data, and that the visual characteristics of the graphics are \textit{equivariant} to their corresponding components under monoid actions. TEAM defines these constraints on the transformation function such that they are not specific to any one type of encoding or visual characteristic. The toy prototype built using this model validates that it is usable for a general purpose visualization tool since it can be iteratively integrated into existing architecture rather than starting from scratch. Factoring out graphic formation into assembly functions allows for much more clarity in how they differ. This prototype demonstrates that this framework can generate the fundamental point (scatter plot) and line (line chart) marks.

>>>>

\begin{document}
\section{Discussion}
The Topological Equivariant Artist Model (TEAM) is a functional model of the structure preserving maps from data to visual representation. TEAM expresses the specifications that graphic and data must have equivalent \textit{continuity} equivalent to the data, and that the visual characteristics of the graphics are \textit{equivariant} to their corresponding components. TEAM expresses these constraints in the encoding \vchannel, assembly \vmark, and reindexing \vindex\ functions that make up the artist \vartist. This decomposition of the artist into smaller components functional pieces allows TEAM to provide well specified guidance on implementing visualization components based on this architecture. The proof of concept prototype built using this model validates that it is usable for a general purpose visualization tool. Additionally, the decomposition facilitates iteratively integrating TEAM into existing architecture rather than starting from scratch, since \vchannel, \vmark\ and \vindex\ functions can be implemented independently. This prototype demonstrates that this framework can generate the fundamental point (scatter plot) and line (line chart) marks. Furthermore, combining Butler's proposal of a fiber bundle model of visualization data with Spivak's formalism of schema lets TEAM support a variety of data continuities, including  discrete relational tables, multivariate high resolution spatio temporal datasets, and complex networks. Although the prototype currently only implements 0D and 1D continuity, we expected it to generalize to the other continuities.
